\documentclass[letterpaper,10pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor}
\usepackage[colorlinks = true, urlcolor = yellow]{hyperref}

% Define colors for dark mode
\definecolor{background}{RGB}{35,35,35}
\definecolor{text}{RGB}{220,220,220}
\definecolor{accent}{RGB}{100,149,237} % Light blue color

% Set page color and text color
\pagecolor{background}
\color{text}

\usepackage{titlesec}
\titleformat{\section}{\large\bfseries\color{accent}}{\thesection}{0.5em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.5em}{0.3em}

\usepackage{enumitem}
\setlist{nolistsep, leftmargin=*}

\input{flag.tex}


% Compact header style
\newcommand{\header}[4]{
    \begin{center}
        \textbf{\Huge{#1}}\\
        \small{
            #2 \hspace{1em}
            \textcolor{accent}{#3} \hspace{1em}
            \href{#4}{GitHub}
        }
    \end{center}
}

\begin{document}


\header{Tassilo Neubauer}{tassilo.neubauer@gmail.com}{+1234567890}{https://github.com/sonofhypnos}

\section*{Education}
\textbf{Karlsruhe Institute of Technology} \hfill Karlsruhe, Germany \\
B.S. Computer Science, Grade Average 3.1 on a scale from 5 (lowest) to 1 (highest) \hfill October 2020--December 2023
\begin{itemize}
    \item \textit{Thesis:} Machine Learning-based Root Cause Analysis for Intelligent Production.
\end{itemize}



\section*{Experience}
\begin{itemize}
    \item \textbf{Freelance Software Developer, BoostX} \hfill Online, June 2024--August 2024
    \begin{itemize}
            \item stub
            % TODO: add real item
    \end{itemize}
    \item \textbf{Freelance Software Developer, Exosome Consulting} \hfill Online, January 2024--June 2024
    \begin{itemize}
        \item Developed data pipelines for efficient data processing and analysis.
    \end{itemize}
    \item \textbf{Research Assistant, Forschungszentrum Informatik} \hfill Karlsruhe, Germany, March 2022--December 2022
    \begin{itemize}
        \item Generated visualization recommendations using evolutionary algorithms.
        \item Combined random forests and simple feedforward neural networks based on artificial feedback.
    \end{itemize}
    \item \textbf{Research Assistant, KIT Political Economy Chair} \hfill Karlsruhe, Germany, September 2021--December 2021
    \begin{itemize}
        \item Optimized online experiment deployment (previously handled by another chair), reducing setup time from weeks to hours
        \item Set up experiment hosting on Heroku and participant recruitment through Prolific
    \end{itemize}
\end{itemize}

\ifdefined\EAVersion
\section*{Extracurriculars}
  \begin{itemize}
      \item {\textbf{Coorganizer of local EA group Karlsruhe}} \hfill April 2021--November 2023 \\
      {Booking rooms, went through the paperwork to become an official university group.}
      \item {\textbf{Member in \href{https://aisafety.com/}{AI-Safety-Reading-Group}}} \hfill October 2019--June 2020 \\
      {Learned about risks from advanced artificial intelligence. Read Human Compatible, Superintelligence and Rationality from AI to Zombies.}
      \item {\textbf{Commenting and occasionally posting on \href{https://www.metaculus.com/accounts/profile/106992/}{Metaculus} and later \href{https://www.lesswrong.com/users/morpheus}{Lesswrong}}} \hfill June 2019--Current \\
      {\textasciitilde{} 2000 predictions on \textasciitilde{} 600 questions on Metaculus. Currently active only on Lesswrong.}
  \end{itemize}
\fi

\unless\ifdefined\EAVersion
	\section*{Skills}
	\noindent\small\textit{Proficiency rated on a scale of 1 (basic) to 3 (high).}
	\normalsize
	\begin{itemize}
		\item \textbf{Programming Languages:} Python (3), Typescript (2), Java (2), C++ (2), SQL (2), Bash (2), C (1), Nix (1), Haskell (1)
		\item \textbf{Software and Libraries:} Emacs (3), React (2), Numpy (2), Pandas (2), Pytorch (2), Latex (1), Make (1)
		\item \textbf{Operating Systems:} Linux (3), Windows (1)
		\item \textbf{Languages:} German (native), English (3), Japanese (1), French (1)
	\end{itemize}
\fi

\section*{Projects}
\begin{itemize}
    \item \textbf{PIBBSS Research Hackathon: Exploring Belief State Steering in Transformer Models} \hfill June 1--3, 2024 \\
      \begin{itemize}
          \item Participated in a 2-day intensive research hackathon with two other collaborators
          \item Explored and implemented an approach using lower-dimensional belief state geometry for steering Transformer models
          \item Applied subspace steering techniques using Moore-Penrose Pseudo-Inverse
          \item Produced a brief technical report summarizing our methods and initial findings
              %#TODO: add my summary
          \item \href{https://github.com/sonofhypnos/CV/blob/main/steering-models-belief-states.pdf}{Project summary}
      \end{itemize}
	\item \href{https://github.com/sonofhypnos/fatebook.el}{fatebook.el}. An Emacs plugin to create and upload predictions to Fatebook. I created the tool for my own use.
	\item \href{https://sonofhypnos.github.io/blog/prediction/python/2021/01/30/sp500.html}{Predicting the S\&P 500} Python, Numpy, Pandas, by sampling from past market data. I used this to win money on the \href{https://www.almanisprivate.com/}{Almanis} prediction market. This method worked better for me than just eyeballing trends.
  \item \textbf{ArmarX Distributed Robot Framework Plugin} \hfill April 2022--September 2022 \\
        Collaborated with a team of four students to develop a C++ GUI plugin for the
        ArmarX distributed robot framework. A standout contribution of mine was the
        design and implementation of a foldable timeline that visually represented the
        robot's hierarchically structured memory over time, leveraging Qt5 for the basic components.
\end{itemize}

\section*{Courses}
\begin{itemize}
    \item \textbf{Math:} Linear Algebra I \& II, Real Analysis I \& II, Probability Theory, Numerical Math for Computer Scientists
    \item \textbf{Computer Science:} Programming (Java), Software Engineering (Java), Programming Paradigms, Databases, Cognitive Systems, Theory of Computer Science I \& II, Algorithms I \& II, Advanced Algorithmic Programming, Operating Systems, Computer Networks among others
    \item \textbf{Physics:} Experimental Physics I \& II, Modern Physics for Computer Scientists
\end{itemize}

\unless\ifdefined\EAVersion
\section*{Extracurriculars}
  \begin{itemize}
      \item {\textbf{Coorganizer of local EA group Karlsruhe}} \hfill April 2021--November 2023 \\
      {Booked rooms, went through the paperwork to become an official university group.}
      \item {\textbf{Member in \href{https://web.archive.org/web/20220123065219/http://aisafety.com/}{AI-Safety-Reading-Group}}} \hfill October 2019--June 2020 \\
      {Learned about risks from advanced artificial intelligence. Read Human Compatible, Superintelligence and Rationality from AI to Zombies.}
      \item {\textbf{Commenting and occasionally posting on \href{https://www.metaculus.com/accounts/profile/106992/}{Metaculus} and later \href{https://www.lesswrong.com/users/morpheus}{Lesswrong}}} \hfill June 2019--Current \\
      {\textasciitilde{} 2000 predictions on \textasciitilde{} 600 questions on Metaculus. Currently active only on Lesswrong.}
  \end{itemize}
\fi

\end{document}
